Software Ticket Quality

### 2017-10-17 proposal/mprop.tex
Added paper on software quality in OSS

>>>>

\textbf{Code Quality Analysis in OSS}\cite{stamelos2002code}:
\begin{itemize}
  \item \textbf{What were the goals?}
    The article tries to discuss and examine the quality of the source code
    delivered by open source projects.
  \item \textbf{What was the method?}
    They used a set of tools that could automatically inspect various aspects
    of source code. The authors analyzed the 6th release of the OpenSUSE project
    and examined only the components, which are defined by C functions in the
    programs.
  \item \textbf{What did they learn?}
    The research's results show that Linux applications have high quality 
    code standards that one might expect in an open source repository, but 
    the quality is lower than the one implied by the standard. More than half
    of the components were in a high state of quality, but on the other hand, 
    most lower quality components cannot be improved only by applying some
    corrective actions. Thus, even though not all the source code was in 
    an industrial standards shape, there is definitely room for further 
    improvement and open source repositories proved to be of good quality.
  \item \textbf{Relevance to our work}: this work completes the previous paper
    on software quality in general by looking specifically at quality in
    open source projects, which will be our main points for data collection.
\end{itemize}
